Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-16 paper/paper.tex
Iterate Concurrency Control introduction

\section{Concurrency Control \tbr}
\label{sec:concurrency-control}

The TrueTime API allows Spanner to guarantee some correctness properties of the
implemented concurrency control. This enables the main features in terms of
transaction, i.e. externally-consistent transactions, lock-free read-only
transactions and so-called \emph{snapshot reads}. Snapshot reads are non-blocking
reads in the past at a specific timestamp $t$. Then, Spanner guarantees that
snapshot reads will see the effects of all transactions committed as of $t$.

Spanner provides different operations as can be seen in
Table~\ref{tbl:reads-writes}. Read-only transactions have to be made explicit.
This requires the application/user to predeclare that the read-only transaction
does not include write operations. Moreover, read-only transaction have the
benefits of snapshot isolation because they are \emph{lock-free}. Standalone
writes are simply read-write transaction without any read operations. Non-snapshot
standalone reads are implemented as read-only transactions. Read-only transactions
and snapshot reads proceed on any \emph{sufficiently up-to-date} replica. For
snapshot reads, the application/user has two options. On the one hand, a precise
timestamp can be specified at which the read should be executed. On the other
hand, an upper bound can be specified and Spanner choses a timestamp that
satisfies this bound.

\begin{table}
  \centering
  \begin{tabular}{|l||l|l|}
    \hline
    {\bfseries Operation} & {\bfseries Concurrency Control} &
    {\bfseries Replica required} \tabularnewline
    \hline\hline
    Read-Write transaction & Pessimistic & leader \tabularnewline
    \hline
    Read-Only transaction & Lock-free & leader; any
    \tabularnewline
    \hline
    Snapshot Read, client-provided timestamp & Lock-free & any \tabularnewline
    \hline
    Snapshot Read, client-provided bound & Lock-free & any \tabularnewline
    \hline
  \end{tabular}
  \caption{Reads and writes in Spanner}
  \label{tbl:reads-writes}
\end{table}

>>>>

\section{Concurrency Control}
\label{sec:concurrency-control}

The TrueTime API allows Spanner to guarantee some correctness properties of the
implemented concurrency control. These enable some of the main features, i.e.
externally-consistent transactions, lock-free read-only transactions and so-called
\emph{snapshot reads}. Snapshot reads are non-blocking reads in the past at a
specific timestamp $t$. In this case, Spanner guarantees that snapshot reads will
see the effects of all transactions committed as of $t$.

Spanner provides different operations, as can be seen in
Table~\ref{tbl:reads-writes}. Read-only transactions have to be made explicit.
This requires the application/user to predeclare that the read-only transaction
does not include write operations. Moreover, read-only transaction have the
benefits of snapshot isolation because they are \emph{lock-free}. Standalone
writes are simply read-write transaction without any read operations. Non-snapshot
standalone reads are implemented as read-only transactions. Read-only transactions
and snapshot reads proceed on any \emph{sufficiently up-to-date} replica. For
snapshot reads, the application/user has two options. On the one hand, a precise
timestamp can be specified at which the read should be executed. On the other
hand, an upper bound can be specified and Spanner choses a timestamp that
satisfies this bound.

\begin{table}
  \centering
  \begin{tabular}{|l||l|l|}
    \hline
    {\bfseries Operation} & {\bfseries Concurrency Control} &
    {\bfseries Replica required} \tabularnewline
    \hline\hline
    Read-Write transaction & Pessimistic & leader \tabularnewline
    \hline
    Read-Only transaction & Lock-free & leader; any
    \tabularnewline
    \hline
    Snapshot Read, client-provided timestamp & Lock-free & any \tabularnewline
    \hline
    Snapshot Read, client-provided bound & Lock-free & any \tabularnewline
    \hline
  \end{tabular}
  \caption{Reads and writes in Spanner.}
  \label{tbl:reads-writes}
\end{table}
